%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Copyright (c) IBM Corp. 2014
% All rights reserved. This program and the accompanying materials
% are made available under the terms of the Eclipse Public License v1.0
% which accompanies this distribution, and is available at
% http://www.eclipse.org/legal/epl-v10.html
%
% Contributors:
%    lschneid
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper, 10pt]{article}

\includeonly{client_api, back_end_api, runtime}

\usepackage[a4paper]{geometry}
\usepackage{times}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage{todonotes}
\usepackage{skv_macros}
\usepackage{listings}

\title{SKV -- Scalable Key/Value Store}
\author{contact: Lars Schneidenbach \\
  schneidenbach@us.ibm.com
}


\lstset{language=C++,
  frame=single, 
  basicstyle=\small, 
  keywordstyle=\color{black},
  commentstyle=\color{green},
  stringstyle=\color{brown},
  breaklines=true,
  morekeywords={ibv_open_device,ibv_alloc_pd,ibv_create_cq,ibv_create_qp,ibv_modify_qp,ibv_post_send,ibv_post_recv,ibv_poll_cq,ibv_reg_mr,
    uint64_t,uint32_t,uint16_t,uint8_t,ibv_free_device_list,ibv_get_device_list,ibv_get_device_name,ibv_dereg_mr,ibv_destroy_qp,ibv_destroy_cq,
    ibv_destroy_cq,ibv_dealloc_pd,ibv_close_device},
}


\begin{document}
\maketitle
\tableofcontents

\section{SKV Overview}\label{sec:overview}
The design of the Scalable Key/Value Store (SKV) is influenced by
Berkeley DB (BDB) key-value interface and the Remote Direct Memory
Access (RDMA) communication paradigm.  

SKV is a parallel client, parallel server, key-value database system
with basic function similar to BDB. SKV storage can be drawn from main
memory of the node of the parallel machine or from a single-node
key/value store that serves as a storage back-end for the distributed
SKV.  Currently, there's a rocksdb back-end available that allows the
storage to be in the file system.

Each node contributing storage (memory) runs a parallel SKV server and
collectively are known as an SKV Server Group. The SKV client library
runs in an MPI parallel environment (a non-MPI library is available
too).  It provides an API and manages the client end of the message
protocol between the client program and the SKV server port.  SKV
clients and SKV servers operate on a request - response model.  Any
valid SKV command can be sent to any SKV server.  The SKV server group
expects to run on a homogeneous parallel machine.  The clients using
the SKV library accessing a SKV server group may run in the server
partition or externally.  There is exactly 1 server running on each
node of a machine allocation.  The SKV library provides a standard
C/C++ API similar to BDB.  Rather than store data to a file, the SKV
library uses a messaging interface to exchange data with the SKV
server group.  The SKV client-server protocol involves short control
messages handled in an RPC style exchange and bulk transfers handled
via an RDMA type exchange.  Client connection to the SKV server group
is managed so that a single connection point provides RDMA access to
all servers across the machine.


\subsection{The Partitioned Data Set}\label{sec:overview:pds}
SKV uses Partitioned Data Set (PDS) to store tables.

The PDS is the primary structure used to organize SKV data in the
storage of a SKV server group.  A PDS is a distributed container of
key-value records.  When a PDS is opened a data structure is returned
which may be shared with other processes via message passing,
broadcast for example, to enable a parallel process to rapidly gain
global access.

The SKV Server that creates a PDS is the PDS root node.  Each SKV
Server uses a unique ID to name the created PDS.  The unique id is
formed in such a way that the SKV Server address is an accessible
component of the Id.  It is up to the creator of the PDS to keep track
of the pds id including any mapping from a name space map.

A PDS is read and written on a record basis.  To access a record, a
key must be provided.  Parts of records may be read or written.
Records may be compressed.  Currently, records are distributed to
nodes based on a hash of the key, then stored in a red-black tree in
memory or handed to the rocksdb back-end.  Every key hashes to exactly
1 node.  A PDS corresponds to a database table and a record
corresponds to a database row.

PIMD client has the ability to request the server group to take a
current snapshot of the data image and save it to persistent storage
on disk at a specified location.  The server group could then be
restarted with the data from a snapshot image.


\include{client_api}
\include{runtime}
\include{back_end_api}
\include{internals}
\end{document}



%%% Local Variables: 
%%% mode: latex
%%% End: 
